Notes on Validated Model Counting \\ Version of \today

### 2022-07-17 doc/mc-notes.tex
Fixed typos

    \makebox[5mm][l]{\tt 1} & \makebox[7mm]{\tt i}   & \makebox[20mm][l]{\tt 1 2 3 0}   &  \makebox[30mm]{}          & \makebox[5mm]{} & \makebox[40mm][l]{Input clause $C_1$}\\
    {\tt 2} & {\tt i}   & {\tt -1 2 0}  &            & & Input clause $C_2$ \\
    {\tt 3} & {\tt p}   & {\tt 4 -1 -2 -3 0}  &            & & Declare $p_4 = \obar{x}_1 \pand \obar{x}_2 \pand \obar{x}_3$ \\
    {\tt 7} & {\tt a}  & {\tt -4 0} & {\tt 6 5 4 1 0} & & Assert $t_1 = \obar{p}_4 = x_1 \lor x_2 \lor x_3$ \\
            & {\tt dc}  & {\tt 1 } & {\tt 3 7 0} & & Delete clause $C_1$\\
    {\tt 8} & {\tt p}   & {\tt 5 1 -2} &              & & Declare $p_5 = x_1 \pand \obar{x}_2$ \\    
    {\tt 11} & {\tt a} & {\tt -5 0} & {\tt 10 9 2 0}  & & Assert $t_2 = \obar{p}_5 = \obar{x}_1 \lor x_2$ \\
            & {\tt dc}  & {\tt 2 } & {\tt 8 11 0} & & Delete clause $C_2$\\
    {\tt 12} & {\tt s}   & {\tt 6 4 5}   & {\tt 4 9 0}  & & Declare $s_6 = \obar{t}_1 \por \obar{t}_2$ \\
    {\tt 15} & {\tt a}  & {\tt -6 0}       & {\tt 7 11 12 0} & & Assert $t_3 = \obar{s}_6 = t_1 \land t_2$ \\
             & {\tt dc}  & {\tt 7}          & {\tt 13 15 0} & & Delete $t_1$\\
             & {\tt dc}  & {\tt 11}         & {\tt 14 15 0} & & Delete $t_2$\\
  \end{tabular}
  \end{center}  
B). Proof Clauses
  \begin{center}
  \begin{tabular}{lcllll}
    \multicolumn{4}{c}{Clause} & & \multicolumn{1}{c}{Explanation} \\
\midrule
    \makebox[5mm][l]{\tt 1} & \makebox[7mm]{}   & \makebox[20mm][l]{\tt 1 2 3 0}   &  \makebox[30mm]{}          & \makebox[5mm]{} & \makebox[40mm][l]{Input clause $C_1$}\\
    {\tt 2} &    & {\tt -1 2 0}  &            & & Input clause $C_2$ \\
    {\tt 3} &   & {\tt 4 1 2 3 0} &     & & Defining clauses for $p_4$ \\
    {\tt 4} &   & {\tt -4 -1 0} &     & & \\
    {\tt 5} &   & {\tt -4 -2 0} &     & & \\
    {\tt 6} &   & {\tt -4 -3 0} &     & & \\
    {\tt 7} &   & {\tt -4 0} & {\tt 6 5 4 1 0} & & Assert $t_1 = \obar{p}_4 = x_1 \lor x_2 \lor x_3$ \\
            & {\tt dc}  & {\tt 1 } & {\tt 3 7 0} & & Delete clause $C_1$\\

@@

\begin{figure}
  A).  CRAT File Contents
  \begin{center}
  \begin{tabular}{llllll}
    \multicolumn{4}{c}{File line} & & \multicolumn{1}{c}{Explanation} \\
\midrule
    \makebox[5mm][l]{\tt 1} & \makebox[7mm]{}   & \makebox[20mm][l]{\tt 1 2 3 0}   &  \makebox[30mm]{}          & \makebox[5mm]{} & \makebox[40mm][l]{Input clause $C_1$}\\
            {\tt 2} & {\tt i}   & {\tt -1 2 0}  &            & & Input clause $C_2$ \\
            {\tt 3} & {\tt p}   & {\tt 4 -2 -3}  &            & & Declare $p_4 = \obar{x}_2 \pand \obar{x}_3$ \\
    {\tt 6} & {\tt p}   & {\tt 5 -1 -4}  &             & & Declare $p_5 = \obar{x}_1 \pand \obar{p}_4$ \\
    {\tt 9} & {\tt p}   & {\tt 6 1 2} &              & & Declare $p_6 = x_1 \pand x_2$ \\    
    {\tt 12} & {\tt s}   & {\tt 7 5 6}   & {\tt 7 10 0}  & & Declare $s_7 = p_5 \por p_6$ \\
    {\tt 15} & {\tt a}  & {\tt 1 -4 0}    & {\tt 4 5 1 0} & & Justify $\obar{x}_1 \rightarrow \obar{p}_4$ \\
    {\tt 16} & {\tt a}  & {\tt 1 7 0}     & {\tt 13 6 15 0} & & Justify $\obar{x}_1 \rightarrow s_7$ \\
    {\tt 17} & {\tt a}  & {\tt -1 7 0}    & {\tt 14 9 2 0} & & Justify $x_1 \rightarrow s_7$ \\
    {\tt 18} & {\tt a}  & {\tt 7 0}       & {\tt 16 17 0}  & & Justify unit clause $t = s_7$ \\
             & {\tt dc}  & {\tt 1}         & {\tt 3 8 10 12 18 0} & & Delete $C_1$\\
             & {\tt dc}  & {\tt 2}         & {\tt 11 7 12 18 0} & & Delete $C_2$\\
  \end{tabular}
  \end{center}  
B). Proof Clauses
  \begin{center}
  \begin{tabular}{llllll}
    \multicolumn{4}{c}{File line} & & \multicolumn{1}{c}{Explanation} \\
\midrule
    \makebox[5mm][l]{\tt 1} & \makebox[7mm]{}   & \makebox[20mm][l]{\tt 1 2 3 0}   &  \makebox[30mm]{}          & \makebox[5mm]{} & \makebox[40mm][l]{Input clause $C_1$}\\
    {\tt 2} &    & {\tt -1 2 0}  &            & & Input clause $C_2$ \\
    {\tt 3} &   & {\tt 4 2 3 0} &     & & Defining clauses for $p_4$ \\
    {\tt 4} &   & {\tt -4 -2 0} &     & & \\
    {\tt 5} &   & {\tt -4 -3 0} &     & & \\
    {\tt 6} &   & {\tt 5 1 4 0} &     & & Defining clauses for $p_5$ \\
    {\tt 7} &   & {\tt -5 -1 0} &     & & \\
    {\tt 8} &   & {\tt -5 -4 0} &     & & \\
    {\tt 9} &   & {\tt 6 -1 -2 0}&     & & Defining clauses for $p_6$ \\ 
    {\tt 10} &   & {\tt -6 1 0}    &  & & \\
    {\tt 11} &   & {\tt -6 2 0}    &  & & \\ 
     &           & {\tt -5 -6}   & {\tt 7 10 0}  & & Mutual exclusion proof for $s_7$ \\
    {\tt 12} &   & {\tt -7 5 6 0}  &     & & Defining clauses for $s_7$ \\ 
    {\tt 13} &   & {\tt  7 -5 0}    &  & & \\  
    {\tt 14} &   & {\tt  7 -6 0}    &  & & \\
    {\tt 15} &   & {\tt 1 -4 0}    & {\tt 4 5 1 0} & & Justify $\obar{x}_1 \rightarrow \obar{p}_4$ \\
    {\tt 16} &   & {\tt 1 7 0}     & {\tt 13 6 15 0} & & Justify $\obar{x}_1 \rightarrow s_7$ \\
    {\tt 17} &   & {\tt -1 7 0}    & {\tt 14 9 2 0} & & Justify $x_1 \rightarrow s_7$ \\
    {\tt 18} &   & {\tt 7 0}       & {\tt 16 17 0}  & & Justify unit clause $t = s_7$ \\
             & {\tt dc}  & {\tt 1}         & {\tt 3 15 0} & & Delete $C_1$\\
             & {\tt dc}  & {\tt 2}         & {\tt 11 7 12 18 0} & & Delete $C_2$\\
  \end{tabular}
  \end{center}  
  \caption{CRAT file \#2B for formula $\phi_2 = (x_1 \lor x_2 \lor x_3) \land (\obar{x}_1 \lor x_2)$, and the resulting set of proof clauses}
  \label{fig:p2-cdcl:crat}
\end{figure}

>>>>

    \makebox[5mm][l]{\tt 1} & \makebox[7mm]{\tt i}   & \makebox[20mm][l]{\tt 1 2 3 0}   &  \makebox[30mm]{}          & \makebox[5mm]{} & \makebox[40mm][l]{Input clause $C_1$}\\
    {\tt 2} & {\tt i}   & {\tt -1 2 0}  &            & & Input clause $C_2$ \\
    {\tt 3} & {\tt p}   & {\tt 4 -1 -2 -3 0}  &            & & Declare $p_4 = \obar{x}_1 \pand \obar{x}_2 \pand \obar{x}_3$ \\
    {\tt 7} & {\tt a}  & {\tt -4 0} & {\tt 6 5 4 1 0} & & Assert $t_1 = \obar{p}_4 = x_1 \lor x_2 \lor x_3$ \\
            & {\tt dc}  & {\tt 1 } & {\tt 3 7 0} & & Delete clause $C_1$\\
    {\tt 8} & {\tt p}   & {\tt 5 1 -2 0} &              & & Declare $p_5 = x_1 \pand \obar{x}_2$ \\    
    {\tt 11} & {\tt a} & {\tt -5 0} & {\tt 10 9 2 0}  & & Assert $t_2 = \obar{p}_5 = \obar{x}_1 \lor x_2$ \\
            & {\tt dc}  & {\tt 2 } & {\tt 8 11 0} & & Delete clause $C_2$\\
    {\tt 12} & {\tt s}   & {\tt 6 4 5}   & {\tt 4 9 0}  & & Declare $s_6 = \obar{t}_1 \por \obar{t}_2$ \\
    {\tt 15} & {\tt a}  & {\tt -6 0}       & {\tt 7 11 12 0} & & Assert $t_3 = \obar{s}_6 = t_1 \land t_2$ \\
             & {\tt dc}  & {\tt 7}          & {\tt 13 15 0} & & Delete $t_1$\\
             & {\tt dc}  & {\tt 11}         & {\tt 14 15 0} & & Delete $t_2$\\
  \end{tabular}
  \end{center}  
B). Proof Clauses
  \begin{center}
  \begin{tabular}{lcllll}
    \multicolumn{4}{c}{Clause} & & \multicolumn{1}{c}{Explanation} \\
\midrule
    \makebox[5mm][l]{\tt 1} & \makebox[7mm]{}   & \makebox[20mm][l]{\tt 1 2 3 0}   &  \makebox[30mm]{}          & \makebox[5mm]{} & \makebox[40mm][l]{Input clause $C_1$}\\
    {\tt 2} &    & {\tt -1 2 0}  &            & & Input clause $C_2$ \\
    {\tt 3} &   & {\tt 4 1 2 3 0} &     & & Defining clauses for $p_4$ \\
    {\tt 4} &   & {\tt -4 -1 0} &     & & \\
    {\tt 5} &   & {\tt -4 -2 0} &     & & \\
    {\tt 6} &   & {\tt -4 -3 0} &     & & \\
    {\tt 7} &   & {\tt -4 0} & {\tt 6 5 4 1 0} & & Assert $t_1 = \obar{p}_4 = x_1 \lor x_2 \lor x_3$ \\
            & {\tt dc}  & {\tt 1 } & {\tt 3 7 0} & & Delete clause $C_1$\\

@@

\begin{figure}
  A).  CRAT File Contents
  \begin{center}
  \begin{tabular}{llllll}
    \multicolumn{4}{c}{File line} & & \multicolumn{1}{c}{Explanation} \\
\midrule
    \makebox[5mm][l]{\tt 1} & \makebox[7mm]{}   & \makebox[20mm][l]{\tt 1 2 3 0}   &  \makebox[30mm]{}          & \makebox[5mm]{} & \makebox[40mm][l]{Input clause $C_1$}\\
            {\tt 2} & {\tt i}   & {\tt -1 2 0}  &            & & Input clause $C_2$ \\
            {\tt 3} & {\tt p}   & {\tt 4 -2 -3 0}  &            & & Declare $p_4 = \obar{x}_2 \pand \obar{x}_3$ \\
    {\tt 6} & {\tt p}   & {\tt 5 -1 -4 0}  &             & & Declare $p_5 = \obar{x}_1 \pand \obar{p}_4$ \\
    {\tt 9} & {\tt p}   & {\tt 6 1 2 0} &              & & Declare $p_6 = x_1 \pand x_2$ \\    
    {\tt 12} & {\tt s}   & {\tt 7 5 6}   & {\tt 7 10 0}  & & Declare $s_7 = p_5 \por p_6$ \\
    {\tt 15} & {\tt a}  & {\tt 1 -4 0}    & {\tt 4 5 1 0} & & Justify $\obar{x}_1 \rightarrow \obar{p}_4$ \\
    {\tt 16} & {\tt a}  & {\tt 1 7 0}     & {\tt 13 6 15 0} & & Justify $\obar{x}_1 \rightarrow s_7$ \\
    {\tt 17} & {\tt a}  & {\tt -1 7 0}    & {\tt 14 9 2 0} & & Justify $x_1 \rightarrow s_7$ \\
    {\tt 18} & {\tt a}  & {\tt 7 0}       & {\tt 16 17 0}  & & Justify unit clause $t = s_7$ \\
             & {\tt dc}  & {\tt 1}         & {\tt 3 8 10 12 18 0} & & Delete $C_1$\\
             & {\tt dc}  & {\tt 2}         & {\tt 11 7 12 18 0} & & Delete $C_2$\\
  \end{tabular}
  \end{center}  
B). Proof Clauses
  \begin{center}
  \begin{tabular}{llllll}
    \multicolumn{4}{c}{File line} & & \multicolumn{1}{c}{Explanation} \\
\midrule
    \makebox[5mm][l]{\tt 1} & \makebox[7mm]{}   & \makebox[20mm][l]{\tt 1 2 3 0}   &  \makebox[30mm]{}          & \makebox[5mm]{} & \makebox[40mm][l]{Input clause $C_1$}\\
    {\tt 2} &    & {\tt -1 2 0}  &            & & Input clause $C_2$ \\
    {\tt 3} &   & {\tt 4 2 3 0} &     & & Defining clauses for $p_4$ \\
    {\tt 4} &   & {\tt -4 -2 0} &     & & \\
    {\tt 5} &   & {\tt -4 -3 0} &     & & \\
    {\tt 6} &   & {\tt 5 1 4 0} &     & & Defining clauses for $p_5$ \\
    {\tt 7} &   & {\tt -5 -1 0} &     & & \\
    {\tt 8} &   & {\tt -5 -4 0} &     & & \\
    {\tt 9} &   & {\tt 6 -1 -2 0}&     & & Defining clauses for $p_6$ \\ 
    {\tt 10} &   & {\tt -6 1 0}    &  & & \\
    {\tt 11} &   & {\tt -6 2 0}    &  & & \\ 
     &           & {\tt -5 -6}   & {\tt 7 10 0}  & & Mutual exclusion proof for $s_7$ \\
    {\tt 12} &   & {\tt -7 5 6 0}  &     & & Defining clauses for $s_7$ \\ 
    {\tt 13} &   & {\tt  7 -5 0}    &  & & \\  
    {\tt 14} &   & {\tt  7 -6 0}    &  & & \\
    {\tt 15} &   & {\tt 1 -4 0}    & {\tt 4 5 1 0} & & Justify $\obar{x}_1 \rightarrow \obar{p}_4$ \\
    {\tt 16} &   & {\tt 1 7 0}     & {\tt 13 6 15 0} & & Justify $\obar{x}_1 \rightarrow s_7$ \\
    {\tt 17} &   & {\tt -1 7 0}    & {\tt 14 9 2 0} & & Justify $x_1 \rightarrow s_7$ \\
    {\tt 18} &   & {\tt 7 0}       & {\tt 16 17 0}  & & Justify unit clause $t = s_7$ \\
             & {\tt dc}  & {\tt 1}         & {\tt 3 15 0} & & Delete $C_1$\\
             & {\tt dc}  & {\tt 2}         & {\tt 11 7 12 18 0} & & Delete $C_2$\\
  \end{tabular}
  \end{center}  
  \caption{CRAT file \#2B for formula $\phi_2 = (x_1 \lor x_2 \lor x_3) \land (\obar{x}_1 \lor x_2)$, and the resulting set of proof clauses}
  \label{fig:p2-cdcl:crat}
\end{figure}
